Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-17 ms.tex
TDE jets

\citet{BergerZauderer+:2012a}  infer a flattening of the gas density profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks qualitiatively similar to that the density profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid line).  Their inferred  gas profile also shows a break at radii $\sim 0.6$ pc, which in our model corresponds to the break radius of the galaxy and hence would imply a SMBH mass of TINY accroding to the mean relationship from the \citet{Lauer+Faber:2007a} sample.  More detailed models for the environment, and the implications of our models for CNM profiles for the diversity of radio emission from TDE jets, will be
explored further in future work.

>>>>

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
qualitiatively similar to that the density profile we predict for core
galaxies (Fig.~\ref{fig:profiles}, solid line), although to obtain
such a flattening on the inferred radial scale, would require a large
$\Mbh\sim 10^7 \Msun$.  Their inferred gas profile also shows a break
at radii $\sim 0.6$ pc, which in our model corresponds to the break
radius of the galaxy and hence would imply an unrealistically small
SMBH mass $\Mbh\simeq 100\Msun$.  accroding to the mean relationship
from the \citet{Lauer+Faber:2007a} sample. A more likely explanation
is that the observed break in the gas density is associated with a
break in a nuclear star cluster in the galaxy {\bf AGs-ref Carson et
  al. 2015.}.

More detailed models for the environment, and the implications of our
models for CNM profiles for the diversity of radio emission from TDE
jets, will be explored further in future work.
